Classical probability measures as pullback of quantum probability measures?

### 2022-04-11 pullback.tex
pullback.tex Exported from pullback.lyx...

\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability-1}
\end{align}
. Since that ``precomposition'' is called ``pullback'' in differential

@@

Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and (\ref{eq:pullback-properties})\tabularnewline

@@

\end{array}$ & \tabularnewline

>>>>

\begin{subequations}\label{eq:CPM-constraints}
 &  & \mu\left(\varphi(\Omega)\right)=\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
 &  & \mu\left(\varphi\left(\overline{E}\right)\right)=\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
 &  & \mu\left(\varphi(\emptyset)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-complement})}}{=}1-\mu\left(\varphi\left(\Omega\right)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-necess})}}{=}0\,,\label{eq:CPM-imposs}
and for each pair of disjoin $E_{0}$ and $E_{1}$: 
\begin{aligned} & \mu\left(\varphi\left(E_{0}\cup E_{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(\emptyset\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\left(\mathbb{1}-\mathbb{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:QuantumProbability-Addition})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)\right)+\mu\left(\varphi\left(E_{1}\right)\right)\,.
\end{aligned}
\label{eq:Probability-Addition}
Since that ``precomposition'' is called ``pullback'' in differential

@@

Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and~(\ref{eq:pullback-properties})\tabularnewline

@@

\end{array}$ & Eqs.~(\ref{eq:CPM-constraints}) and~(\ref{eq:Probability-Addition})\tabularnewline
